Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-31 p2/ordering.tex
Todo flags

\begin{mylem}\mlabel{connected_changes}
Given a set of commands that
does not contain assertion commands,
and which can be applied to a filesystem in some order without breaking it,
and which contains commands on $n$ and $\nn$ where $\nn\descendant n$,
then the set must also contain a command
on each node between $n$ and $\nn$.
\end{mylem}
\begin{proof}
Without loss of generality, we can assume that $\nn\neq\parent(n)$.
We prove that under the given conditions, the set must contain a command on $\parent(n)$.
Then, by reapplying this result, we know that the set must contain commands on every
ancestor of $n$ up to $\nn$.

@@

\begin{mylem}\mlabel{simple_reorder_equiv}
For a simple sequence $\wrksx{S}$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
\[ \orderset{S} = [S]_\equiv \cap \setssmp, \]
where $\setssmp$ is the set of all simple sequences.
\end{mylem}

>>>>

\begin{mylem}\mlabel{connected_changes}
Given a set of commands that
does not contain assertion commands,
and which can be applied to a filesystem in some order without breaking it,
and which contains commands on $n$ and $\nn$ where $\nn\descendant n$,
then the set must also contain a command
on each node between $n$ and $\nn$.
\end{mylem}
\begin{proof}
TODO: If something changes, everything changes up to the leaves.

Without loss of generality, we can assume that $\nn\neq\parent(n)$.
We prove that under the given conditions, the set must contain a command on $\parent(n)$.
Then, by reapplying this result, we know that the set must contain commands on every
ancestor of $n$ up to $\nn$.

@@

\begin{mylem}\mlabel{simple_reorder_equiv}
For a simple sequence $\wrksx{S}$,
$\orderset{S}$ is the set of all simple sequences equivalent to $S$, that is,
\[ \orderset{S} = \{T \whr T\equiv S \wedge T \mbox{~is simple} \}. \]
\end{mylem}

### 2017-10-31 p2/paper.tex
Updated URL, improved documentation
Inverses are no longer needed
Fixed the soundness proof. Inverses are needed after all.
Output labels for easier reviewing
New parent function symbol
Todo flags

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{centernot}
\usepackage{tikz}
\usepackage[capitalise]{cleveref}

@@

\title{Algebraic File Synchronization: Adequacy and Completeness}
\author{Elod Pal Csirmaz\\
\texttt{\rot{\rot{maz.}{csir}{ep}com}{@}{elod}}}

@@

@@

\bigskip\noindent
{\bf Keywords:} % (4-6)
file synchronization,
algebraic approach,
distributed systems,
reconciliation,
data replication
% conflict detection,
% operation-based 
% conflict resolution
% computer algebra

@@

\section{Definitions}\label{sec_def}

@@

\section{Update Detection}\label{sec_update}

@@

\section{Reconciliation}\label{sec_rec}

@@

I thank Laszlo Csirmaz for his invaluable input on this paper,
and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{centernot}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage[capitalise,poorman,nameinlink]{cleveref}

@@

\title{Algebraic File Synchronization: Adequacy and Completeness}
\author{Elod Pal Csirmaz\\
\texttt{\rot{\rot{maz.}{csir}{ep}com}{@}{elod}}}
\date{}

@@

TODO: $n'$ should always be parent(n).

TODO: Theorem 1, S' extends S. ... All S is extended by simple sequence, and generate with inference rules.

TODO: Explain what happens to FF commands.

@@

\bigskip\noindent
{\bf Keywords:} % (4-6)
file synchronization,
algebraic approach,
distributed systems,
reconciliation,
data replication
% conflict detection,
% conflict resolution
% computer algebra

@@

\section{Definitions}\mlabel{sec_def}

@@

\section{Update Detection}\mlabel{sec_update}

@@

\section{Reconciliation}\mlabel{sec_rec}

@@

% TODO Add reviewer
% TODO Consider below
I thank L. Csirmaz for his invaluable input on this paper,
and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.
